Students must abide by the code of conduct.
Here are a few rules from the Dixie Technical
College Student Code of Conduct:
\begin{itemize}
    \item Destruction of Property: Intentionally
    or recklessly damaging, destroying, defacing,
    or tampering with the property of Dixie Tech
    or the property of another person or entity. 
    \item Drugs, Alcohol, and Tobacco (See the Drug,
    Alcohol and Tobacco Free Campus Policy): Dixie Tech
    is committed to upholding all local, state, and
    federal laws regarding drug, alcohol, and tobacco use.
    Students will be required to abide by these laws as
    well as the Dixie Tech Drug, Alcohol, and Tobacco
    Free Campus Policy which states that students may
    not manufacture, dispense, possess, sell, distribute,
    use or be under the influence of any controlled
    substance or alcohol on Dixie Tech property,
    while on an externship, or while participating in
    any Dixie Tech affiliated event on or off- campus.
    If a student is tested upon reasonable suspicion
    and tests positive for alcohol or any controlled
    substance, the student shall be considered to be
    under the influence, regardless of any prescriptions
    the student may have.
    \item Information Technology Abuse: Misuse of, theft,
    unauthorized access or abuse of Dixie Tech information
    technology including the violation of College Network
    Resources Acceptable Use Policy. 
    \item Insubordination: Willful or intentional failure
    to obey a lawful and reasonable request of an instructor
    or administrator, or an action which constitutes lack of
    respect or harassment directed toward an instructor or supervisor. 
\end{itemize}
For a complete list of student requirements, click here to review
the entire
\href{https://dixietech.edu/wp-content/uploads/files/policies/student-code-of-conduct.pdf}{Student Code of Conduct}
on the website.
