\textbf{Code Ownership:} In most courses, all code written by the student is owned by the student.
In the Group Project course, all code written by the student for a client is owned by the client.
\par
\bigskip
\textbf{ADA policy and students with disabilities:} In accordance with Section 504 of the Rehabilitation
Act and the Americans with Disabilities Act (“ADA”), Dixie Tech offers accommodations to students
with documented learning, medical, physical and/or psychological disabilities. It is your responsibility to
contact the Disability Services Coordinator, preferably prior to the beginning of the course, to initiate the
accommodation process and to notify instructors as soon as possible so accommodations can be made
early on in the course.
\par
\bigskip
Reasonable accommodations will be made to allow each student to meet course requirements. Should
you need assistance or accommodations, please contact Student Services.
\par
\bigskip
\textbf{Dixie Tech is a tobacco-free campus:} Please leave campus to use tobacco or vaping products.
\par
\bigskip
\textbf{Student code of conduct:} By attending, you agree to follow the Dixie Tech student code of conduct.
A copy of this form can be requested from your instructor or it can be found on the Dixie Tech website.
You will be held accountable for everything on this document so please become familiar with it.
\par
\bigskip
\textbf{Cheating:} Cheating is a serious offense and will be punished by penalties deemed appropriate by the
administration. Repeat offenders may be expelled from the program.
\par
\bigskip
\textbf{Plagiarism:} Plagiarism is considered a form of cheating. Violations of copyright law including plagiarism,
illegal duplication or modification of materials, downloading or uploading copyrighted files without
appropriate permission, and using college equipment for these purposes will be punished.
